---
title: "Journal (reproducible report)"
author: "Nishanth Anand Muthya"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Box Office API

Last compiled: `r Sys.Date()`

Box Office Mojo is a website similar to IMDB that provides the list and information about movies, their rating, release date and lifetime gross for the top 200 movies.

```{r}
cat("\014")

# WEBSCRAPING ----

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)      #GET() function
library(knitr)

# 2 COLLECT movie information ----
url  <- "https://www.boxofficemojo.com/chart/top_lifetime_gross/?area=XWW"

# Read in the HTML for the entire webpage
html <- url %>% 
        read_html()

# Web scrape the ids for the families

rank <- html %>% 
        html_nodes(".a-text-right.mojo-header-column.mojo-truncate.mojo-field-type-rank") %>% 
        html_text() %>% 
        # Make all values numeric
        as.numeric()


title <-html %>% 
        html_nodes(".mojo-field-type-title > a") %>% 
        html_text() 


link <- html %>%
        html_nodes(".mojo-field-type-title > a") %>% 
        html_attr("href")


release_year <- html %>%
                html_nodes(css = ".a-text-left.mojo-field-type-year") %>%
                html_text() %>%
                enframe(name = "index", value = "release_year") %>%
                slice(2:201)


lifetime_gross <-  html %>%
                   html_nodes(css = ".a-text-right.mojo-field-type-money") %>%
                   html_text() %>%
                   enframe(name = "position", value = "lifetime_gross") %>%
                   slice(2:201)

#3 Joining data
box_office_mojo_database <- tibble(title,rank,link,release_year,lifetime_gross) %>%

mutate(url = glue("https://www.boxofficemojo.com/{link}")) %>%
  
  select(rank,title, release_year, lifetime_gross,url)

kable(box_office_mojo_database, caption = "Box Office Mojo Top Lifetime Grosses")
```


# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.